\begin{thanks}

This thesis could never come out without the support and help from lots of people. I would like to express my gratitude to these listed in the following and many others I might not mention.

First of all, I would thank Prof. Cheng Li, who has been my adviser since I was a undergraduate student. He introduced me to this field and provided the great opportunity to participate the BES\uppercase\expandafter{\romannumeral3} eTOF upgrade and the STAR MTD programs. I appreciate his continuous supervision and support in the last seven years. My gratitude also goes to Prof. Lijuan Ruan who is the co-advisor of my PhD research. She guided me all the analysis details throughout the thesis. I am impressive by her numerous ideas and enthusiasm on the research. I have benefited so much from the day-to-day discussion with her in the last three and half years. I would like to thank Prof. Zhangbu Xu for offering the opportunity to study at BNL, the wonderful place for relativistic heavy-ion physics research. He also guided me the details of THGEM related work and helped me a lot in my analysis. I have learned a lot from the tons of fruitful discussions with him. I also appreciate Prof. Hongfang Chen for her support and encouragement. She, as a scientist and a mentor, sets an example to young people.

My special thanks goes to Prof. Zebo Tang, who introduced me to the heavy-ion physics filed. He guided me the cosmic ray analysis at the very beginning, which started my STAR journey. He always answers my questions with patience no matter how silly they may have been. My special thanks also goes to Dr. Bingchu Huang who taught me a lot in my analysis, MTD related works and lots of technical skills. He also helped me a lot on my living at BNL. I would like to express my gratitude to Dr. Yongjie Sun who guided me on manufacturing and testing MRPC modules.

I would like to thank Dr. Wangmei Zha, and Dr. Chi Yang for pleasant cooperation on installing and commissioning MTD system and lots of helpful discussions on physics and other things. I would like to thank Dr. Hongwei Ke who taught me a lot on coding and understanding STAR software. I also would like to thank Dr. Yi Guo for his discussions and assistances in my analysis. I would like to thank Yifei Xu and Jinlong Zhang, my roommates at BNL, for enjoyable corporation on work, living and abundant helpful discussions. 

I would like to thank the MTD group, dielectron group, light flavor physics working group in STAR Collaboration, especially Dr. Rongrong Ma, Dr. Takahito Todoroki, Prof. Xin Dong, Prof. Frank Geurts, Joey Butterworth and Liwen Wen. I appreciate many assistances from the High Energy Physics Group at USTC, especially Prof. Zizong Xu, Prof. Xiaolian Wang, Prof. Ming Shao, Prof. Qun Wang, Prof. Yifei Zhang, Dr. Yi Zhou, Dr. Tianxiang Chen, Hui Zhang, Kun Jiang, Yuxiang Zhao, Lailin Xu, Xiaozhuang Wang, Yinying Zhu, Rongxing Yang, Wenhao You, Xiaokun Zhao, Shenghui Zhang, and Guannan Xie. I also would like to thank Dr. Xiangli Cui, Dr. Liang Zheng, Dr. Xueye Hu, Dr. Qiye Shou, Qian Yang, Long Zhou, Zhengqiao Zhang, Xiaoxuan Chu, Zhen Liu, Zaochen Ye, Bo Gao, Xinjie Huang, Zhao Feng, Xu Wang, and Chensheng Zhou. We live at BNL like a family and our life is full of happiness every day. I also would like to express my thanks to non-group member Chenshuo Fu and Zhe Zhou for their friendship and joyful memories together.

Finally, I express my deep gratitude to my dear family. I would like to thank my parents for their selfless dedication, infinite love and unconditional support.  I would not be where I am today without them. I would like to thank my wife, Ying He, who has supported and encouraged me all the time. I am forever thankful for her great understanding. I would like to thank my sister for her continuous support and understanding.
\end{thanks}
