%\renewcommand{\baselinestretch}{0.5}
\begin{thebibliography}{10}

\bibitem{QCDtheory}
H. Fritzsch and M. Gell-Mann,
\newblock ``Current algebra: Quarks and what else?''
\newblock {\em Proceedings of the XVI International Conference on High Energy Physics. C720906V2, 135 (1972)}.

\bibitem{DISasymptotic}
D.W. Duke and R.G. Roberts,
\newblock ``Deep inelastic scattering and asymptotic freedom: A detailed analysis and confrontation.''
\newblock {\em Nucl. Phys. B 166, 243 (1980)}.

\bibitem{runningExp}
S. Bethke,
\newblock ``The 2009 world average of $\alpha_{s}$.''
\newblock {\em Eur. Phys. J. C 64, 689 (2009)}.

\bibitem{LQCDPhaseTransistion}
F. Karsch, E. Laermann, and A. Peikert,
\newblock ``The pressure in 2, 2+1 and 3 ﬂavour QCD.''
\newblock {Phys. Lett. B 478, 447 (2000)}.

\bibitem{CriticalPoint}
Z. Fodor and S.D. Katz,
\newblock ``Critical point of QCD at finite $T$ and $\mu$, lattice results for physical quark masses.''
\newblock {JHEP 0404, 050 (2004)}.

\bibitem{BESI}
B. I. Abelev {\it et al.} (STAR Collaboration),
\newblock ``Experimental Study of the QCD Phase Diagram \& Search for the Critical Point: Selected Arguments for the Run-10 Beam Energy Scan.''
\newblock {\em STAR Internal Note: SN0493 (2009)}.

\bibitem{BESII}
L. Adamczyk {\it et al.} (STAR Collaboration),
\newblock ``Studying the Phase Diagram of QCD Matter at RHIC.''
\newblock {\em STAR Internal Note: SN0598 (2014)}.

\bibitem{STARwp}
J. Adams {\it et al.} (STAR Collaboration),
\newblock ``Experimental and theoretical challenges in the search for the quark–gluon plasma: The STAR Collaboration's critical assessment of the evidence from RHIC collisions.''
\newblock {\em Nucl. Phys. A 757, 102 (2005)}.

\bibitem{PHENIXwp}
K. Adcox {\it et al.} (PHENIX Collaboration),
\newblock ``Formation of dense partonic matter in relativistic nucleus–nucleus collisions at RHIC: Experimental evaluation by the PHENIX Collaboration.''
\newblock {\em Nucl. Phys. A 757, 184 (2005)}.

\bibitem{PHOBOSwp}
B.B. Back {\it et al.} (PHOBOS Collaboration),
\newblock ``The PHOBOS perspective on discoveries at RHIC.''
\newblock {\em Nucl. Phys. A 757, 28 (2005)}.

\bibitem{BRAHMSwp}
I. Arsene {\it et al.} (BRAHMS Collaboration),
\newblock ``Quark–gluon plasma and color glass condensate at RHIC? The perspective from the BRAHMS experiment.''
\newblock {\em Nucl. Phys. A 757, 1 (2005)}.

\bibitem{InitialDilepton}
R. Rapp and E. Shuryak,
\newblock ``Thermal dilepton radiation at intermediate masses at the CERN-SpS.''
\newblock {\em Phys. Lett. B 473, 13 (2000)}.

\bibitem{JpsiDeconfinement}
T. Matsui adn H. Satz,
\newblock ``J/$\psi$ suppression by quark-gluon plasma formation.''
\newblock {\em Phys. Lett. B 178, 416 (1986)}.

\bibitem{lifetime_cal}
R. Rapp and H. van Hees,
\newblock ``Thermal dileptons as fireball thermometer and chronometer.''
\newblock {\em Phys. Lett. B 753, 586 (2016)}.

\bibitem{rhopeak}
Ulrich Heinz and Kang Seog Lee,
\newblock ``The $\rho$-peak in the dimuon spectrum as a clock for fireball lifetimes in relativistic nuclear collisions.''
\newblock {\em Phys. Lett. B 259, 162 (1991)}.

\bibitem{dropmass}
G.E. Brown and M. Rho,
\newblock ``Chiral restoration in hot and/or dense matter.''
\newblock {\em Phys. Rep. 269, 333 (1996)}.

\bibitem{broaden0}
R. Rapp and J. Wambach,
\newblock ``Low-Mass Dileptons at the CERN-SPS: Evidence for Chiral Restoration?''
\newblock {\em Eur. Phys. J. A 6, 415 (1999)}.

\bibitem{broaden1}
R. Rapp,
\newblock ``Signatures of thermal dilepton radiation at ultrarelativistic energies.''
\newblock {\em Phys. Rev. C 63, 054907 (2001)}.

\bibitem{broaden2}
R. Rapp and J. Wambach,
\newblock ``Chiral Symmetry Restoration and Dileptons in Relativistic Heavy-Ion Collisions.''
\newblock {\em Adv. Nucl. Phys. 25, 1 (2002)}.

\bibitem{broaden3}
H. van Hees and R. Rapp,
\newblock ``Dilepton Radiation at the CERN Super Proton Synchrotron.''
\newblock {\em Nucl. Phys. A 806, 339 (2008)}.

\bibitem{broaden4}
R. Rapp,
\newblock ``Dilepton Spectroscopy of QCD Matter at Collider Energies.''
\newblock {\em Adv. High Energy Phys. 2013, 148253 (2013)}.

\bibitem{broaden:PHSD0}
W. Cassing and E. L. Bratkovskaya,
\newblock ``Parton–hadron–string dynamics: An off-shell transport approach for relativistic energies.''
\newblock {\em Nucl. Phys. A 831, 215 (2009)}.

\bibitem{broaden:PHSD1}
E. L. Bratkovskaya {\it et al.},
\newblock ``Parton–Hadron-String Dynamics at relativistic collider energies.''
\newblock {\em Nucl. Phys. A 856, 162 (2011)}.

\bibitem{dileptonMed0}
H.J. Xu {\it et al.},
\newblock ``Di-electron production from vector mesons with medium modifications in heavy ion collisions.''
\newblock {\em Phys. Rev. C 85, 024906 ( 2012)}.

\bibitem{dileptonMed1}
G. Vujanovic {\it et al.},
\newblock ``Dilepton production in high energy heavy ion collisions with 3+1 D relativistic viscous hydrodynamics.''
\newblock {\em Nucl. Phys. A 904-905, 557c ( 2013)}.

\bibitem{dileptonMed2}
G. Vujanovic {\it et al.},
\newblock ``Dilepton emission in high-energy heavy-ion collisions with viscous hydrodynamics.''
\newblock {\em Phys. Rev. C 89, 034904 ( 2014)}.

\bibitem{LMRDileptonTheory}
R. Rapp, J. Wambach, and H. van Hees,
\newblock ``The Chiral Restoration Transition of QCD and Low Mass Dileptons.''
\newblock {\em 	arXiv:0901.3289}.

\bibitem{DLS:dielectron0}
H. Z. Huang {\it et al.} (DLS Collaboration),
\newblock ``Dielectron yields in $p+d$ and $p+p$ collisions at 4.9 GeV.''
\newblock {\em 	Phys. Lett. B 297, 233 (1992)}.

\bibitem{DLS:dielectron1}
R. J. Porter {\it et al.} (DLS Collaboration),
\newblock ``Dielectron Cross Section Measurements in Nucleus-Nucleus Reactions at 1.0A GeV.''
\newblock {\em Phys. Rev. Lett. 79, 1229 (1997)}.

\bibitem{HADES:dielectron0}
G. Agakichiev {\it et al.} (HADES Collaboration),
\newblock ``Dielectron Production in $^{12}$C + $^{12}$C Collisions at 2A GeV with the HADES Spectrometer.''
\newblock {\em Phys. Rev. Lett. 98, 052302 (2007)}.

\bibitem{HADES:dielectron1}
G. Agakichiev {\it et al.} (HADES Collaboration),
\newblock ``Study of dielectron production in C + C collisions at 1 A GeV.''
\newblock {\em Phys. Lett. B 663, 43 (2008)}.

\bibitem{HADES:dielectron2}
G. Agakichiev {\it et al.} (HADES Collaboration),
\newblock ``Origin of the low-mass electron pair excess in light nucleus-nucleus collisions.''
\newblock {\em Phys. Lett. B 690, 118 (2010)}.

\bibitem{HADES:dielectron3}
G. Agakichiev {\it et al.} (HADES Collaboration),
\newblock ``Dielectron production in Ar + KCl collisions at 1.76A GeV.''
\newblock {\em Phys. Rev. C 84, 014902 (2011)}.

\bibitem{HELIOS:dimuon}
A. L. S. Angelis {\it et al.} (HELIOS/3 Collaboration),
\newblock ``Excess of continuum dimuon production at masses between threshold and the J/$\psi$ in S–W interactions at 200 GeV/$c$/nucleon.''
\newblock {\em Eur. Phys. J. C 13, 433 (2000)}.

\bibitem{NA38:dimuon}
M. C.  Abreu {\it et al.} (NA38 Collaboration),
\newblock ``Muon pair and vector meson cross-sections in p-W and S-U collisions at 200 GeV/nucleon.''
\newblock {\em Phys. Letter. B 368, 230 (1996)}.

\bibitem{NA50:dimuon}
M. C.  Abreu {\it et al.} (NA38 and NA50 Collaboration),
\newblock ``Dimuon and charm production in nucleus-nucleus collisions at the CERN-SPS.''
\newblock {\em Eur. Phys. J. C 14, 443 (2000)}.

\bibitem{CERES:experiment}
R. Baur {\it et al.},
\newblock ``The CERES RICH detector system.''
\newblock {\em Nucl. Instr. Meth. A 343, 87 (1994)}.

\bibitem{CERES:dielectron0}
G. Agakichiev {\it et al.} (CERES Collaboration),
\newblock ``Enhanced Production of Low-Mass Electron Pairs in 200 GeV/Nucleon S-Au Collisions at the CERN Super Proton Synchrotron.''
\newblock {\em Phys. Rev. Lett. 75, 1272 (1995)}.

\bibitem{CERES:dielectron1}
G. Agakichiev {\it et al.} (CERES Collaboration),
\newblock ``Systematic study of low-mass electron pair production in p–Be and p–Au collisions at 450 GeV/$c$.''
\newblock {\em Eur. Phys. J. C 4, 231 (1998)}.

\bibitem{CERES:dielectron2}
D. Adamova {\it et al.} (CERES Collaboration),
\newblock ``Enhanced Production of Low-Mass Electron-Positron Pairs in 40-A GeV Pb-Au Collisions at the CERN SPS.''
\newblock {\em Phys. Rev. Lett. 91, 042301 (2003)}.

\bibitem{CERES:dielectron3}
G. Agakichiev {\it et al.} (CERES Collaboration),
\newblock ``$e^{+}e^{-}$-pair production in Pb-Au collisions at 158 GeV per nucleon.''
\newblock {\em Eur. Phys. J. C 41, 513 (2005)}.

\bibitem{NA60:dimuon0}
R. Arnaldi {\it et al.} (NA60 Collaboration),
\newblock ``First Measurement of the $\rho$ Spectral Function in High-Energy Nuclear Collisions.''
\newblock {\em Phys. Rev. Lett. 96, 162302 (2006)}.

\bibitem{NA60:dimuon1}
R. Arnaldi {\it et al.} (NA60 Collaboration),
\newblock ``Evidence for Radial Flow of Thermal Dileptons in High-Energy Nuclear Collisions.''
\newblock {\em Phys. Rev. Lett. 100, 022302 (2008)}.

\bibitem{NA60:dimuon2}
R. Arnaldi {\it et al.} (NA60 Collaboration),
\newblock ``Evidence for the production of thermal muon pairs with masses above 1 GeV/$c^{2}$ in 158 A GeV indium-indium collisions.''
\newblock {\em Eur. Phys. J. C 59, 607 (2009)}.

\bibitem{NA60:dimuon3}
R. Arnaldi {\it et al.} (NA60 Collaboration),
\newblock ``NA60 results on thermal dimuons.''
\newblock {\em Eur. Phys. J. C 61, 711 (2009)}.

\bibitem{NA60:dimuon4}
H.J. Specht (for the NA60 Collaboration),
\newblock ``Thermal Dileptons from Hot and Dense Strongly Interacting Matter.''
\newblock {\em AIP Conf. Proc. 1322, 1 (2010)}.

\bibitem{NA60:dimuon5}
S Damjanovic (for the NA60 Collaboration),
\newblock ``Thermal dileptons at SPS energies.''
\newblock {\em J. Phys. G : Nucl. Part. Phys. 35, 104036 (2008)}.

\bibitem{PHENIX:overview}
K. Adcox {\it et al.} (PHENIX Collaboration),
\newblock ``PHENIX detector overview.''
\newblock {\em Nucl. Instr. Meth. A 499, 469 (2003)}.

\bibitem{PHENIX:HBD}
W. Anderson {\it et al.},
\newblock ``Design, construction, operation and performance of a Hadron Blind Detector for the PHENIX experiment.''
\newblock {\em Nucl. Instr. Meth. A 646, 35 (2011)}.

\bibitem{PHENIX:dielectron0}
A. Adare {\it et al.} (PHENIX Collaboration),
\newblock ``Detailed measurement of the $e^{+}e^{-}$ pair continuum in $p$ + $p$ and Au + Au collisions at $\sqrt{s_{NN}}$ = 200 GeV and implications for direct photon production.''
\newblock {\em Phys. Rev. C 81, 034911 (2010)}.

\bibitem{PHENIX:dielectron1}
A. Adare {\it et al.} (PHENIX Collaboration),
\newblock ``Dielectron production in Au+Au collisions at $\sqrt{s_{NN}}$ = 200 GeV.''
\newblock {\em 	arXiv:1509.04667}.

\bibitem{STAR:dielectron0}
L. Adamczyk {\it et al.} (STAR Collaboration),
\newblock ``Di-electron spectrum at mid-rapidity in $p+p$ collisions at $\sqrt{s_{NN}}$ = 200 GeV.''
\newblock {\em Phys. Rev. C 86, 024906 (2012)}.

\bibitem{STAR:dielectron1:PRL}
L. Adamczyk {\it et al.} (STAR Collaboration),
\newblock ``Dielectron Mass Spectra from Au + Au Collisions at $\sqrt{s_{NN}}$ = 200 GeV.''
\newblock {\em Phys. Rev. Lett. 113, 022301 (2014)}.

\bibitem{STAR:dielectron1}
L. Adamczyk {\it et al.} (STAR Collaboration),
\newblock ``Measurements of Dielectron Production in Au+Au Collisions at $\sqrt{s_{NN}} =$ 200 GeV from the STAR Experiment.''
\newblock {\em Phys. Rev. C 92, 24912 (2015)}.

\bibitem{STAR:dielectron2}
L. Adamczyk {\it et al.} (STAR Collaboration),
\newblock ``Energy dependence of acceptance-corrected dielectron excess mass spectrum at mid-rapidity in Au+Au collisions at $\sqrt{s_{NN}}$ = 19.6 and 200 GeV.''
\newblock {\em Phys. Lett. B 750, 64 (2015)}.

\bibitem{ALICE:dielectron}
M. K. Kohler (for the ALICE Collaboration),
\newblock ``Dielectron measurements in pp, p–Pb and Pb–Pb collisions with ALICE at the LHC.''
\newblock {\em Nucl. Phys. A 931, 665 (2014)}.

% chapter 2 (Experimental Setup)
\bibitem{RHIC_Overview}
M. Harrison {\it et al.},
\newblock ``RHIC project overview.''
\newblock {\em Nucl. Instr. Meth. A 499, 235 (2003)}.

\bibitem{RHIC_Configuration}
RHIC Accelerator Division,
\newblock ``RHIC Configuration Manual.''
\newblock {\em https://www.bnl.gov/cad/accelerator/docs/pdf/RHICConfManual.pdf}.

\bibitem{RHIC_Spin}
E.C. Aschenauer {\it et al.},
\newblock ``The RHIC Spin Program: Achievements and Future Opportunities.''
\newblock {\em arXiv:1304.0079}.

\bibitem{eRHIC}
E.C. Aschenauer {\it et al.},
\newblock ``eRHIC Design Study: An Electron-Ion Collider at BNL.''
\newblock {\em arXiv:1409.1633}.

\bibitem{EIC_Physics}
A. Accardi {\it et al.},
\newblock ``Electron Ion Collider: The Next QCD Frontier - Understanding the glue that binds us all.''
\newblock {\em arXiv:1212.1701}.

\bibitem{STARdet}
K.H. Ackermann {\it et al.} (STAR Collaboration),
\newblock ``STAR detector overview.''
\newblock {\em Nucl. Instr. Meth. A 499, 624 (2003)}.

\bibitem{HFTdet}
 D. Beavis {\it et al.},
\newblock ``The STAR Heavy Flavor Tracker Technical Design Report.''
\newblock {\em https://drupal.star.bnl.gov/STAR/starnotes/public/sn0600}.

\bibitem{D0plot}
G. Contin (for the STAR Collaboration),
\newblock ``The STAR Heavy Flavor Tracker and Upgrade Plan.''
\newblock {\em Quark Matter 2015 proceedings}.

\bibitem{TPCdet}
M. Anderson {\it et al.},
\newblock ``The STAR time projection chamber: a unique tool for studying high multiplicity events at RHIC.''
\newblock {\em Nucl. Instr. Meth. A 499, 659 (2003)}.

\bibitem{TPClaser}
J. Abele {\it et al.},
\newblock ``The laser system for the STAR time projection chamber.''
\newblock {\em Nucl. Instr. Meth. A 499, 692 (2003)}.

\bibitem{TOFdet}
The STAR TOF Collaboration,
\newblock ``Proposal for a large area Time of Flight system for STAR.''
\newblock {\em https://drupal.star.bnl.gov/STAR/starnotes/public/sn0621}.

\bibitem{BEMCdet}
M. Beddo {\it et al.},
\newblock ``The STAR Barrel Electromagnetic Calorimeter.''
\newblock {\em Nucl. Instr. Meth. A 499, 725 (2003)}.

\bibitem{MTDdet}
L. Ruan {\it et al.},
\newblock ``Perspectives of a Midrapidity Dimuon Program at RHIC: A Novel and Compact Muon Telescope Detector.''
\newblock {\em J. Phys. G 36, 095001 (2009)}.

\bibitem{BBCdet}
C. A. Whitten Jr. (for the STAR Collaboration),
\newblock ``The Beam-Beam Counter: A Local Polarimeter at STAR.''
\newblock {\em AIP Conference Proceedings 980 (1), 390 (2008)}.

\bibitem{VPDdet}
W.J Llope {\it et al.},
\newblock ``The STAR Vertex Position Detector.''
\newblock {\em Nucl. Instr. Meth. A 759, 23 (2014)}.

\bibitem{ZDCdet}
C. Adler {\it et al.},
\newblock ``The RHIC zero degree calorimeters.''
\newblock {\em Nucl. Instr. Meth. A 470, 488 (2001)}.

\bibitem{Bichsel}
H. Bichsel,
\newblock ``A method to improve tracking and particle identification in TPCs and silicon detectors.''
\newblock {\em Nucl. Instr. Meth. A 562, 154 (2006)}.

\bibitem{STARTOFmrpc0}
M. Shao {\it et al.},
\newblock ``Beam test results of two kinds of multi-gap resistive plate chambers.''
\newblock {\em Nucl. Instr. Meth. A 492, 344 (2002)}.

\bibitem{STARTOFmrpc1}
B. Bonner {\it et al.},
\newblock ``A single Time-of-Flight tray based on multigap resistive plate chambers for the STAR experiment at RHIC.''
\newblock {\em Nucl. Instr. Meth. A 508, 181 (2003)}.

\bibitem{ALICETOFmrpc}
E. Cerron Zeballos {\it et al.},
\newblock ``A new type of resistive plate chamber: The multigap RPC.''
\newblock {\em Nucl. Instr. Meth. A 374, 132 (1996)}.

\bibitem{VPDTOFcalib0}
L.J. Ruan,
\newblock ``Pion, Kaon, Proton and Antiproton Spectra in $d$ + Au and $p$ + $p$ Collisions
at $\sqrt{s_{NN}}$ = 200 GeV at the Relativistic Heavy Ion Collider.''
\newblock {\em Ph. D. Thesis, University of Science and Technology of China (2004)}.

\bibitem{VPDTOFcalib1}
B.C Huang,
\newblock ``Di-lepton production measurements in $p$ + $p$ and Au + Au collisions at RHIC.''
\newblock {\em Ph. D. Thesis, University of Science and Technology of China (2011)}.

\bibitem{tofpid}
M. Shao {\it et al.},
\newblock ``Extensive particle identiﬁca tion with TPC and TOF at the STAR experiment.''
\newblock {\em Nucl. Instr. Meth. A 558, 419 (2006)}.

\bibitem{STARmagnet}
F. Bergsma {\it et al.},
\newblock ``The STAR detector magnet subsystem.''
\newblock {\em Nucl. Instr. Meth. A 499, 633 (2003)}.

% Chapter3 (MTD)
\bibitem{MTDmrpc0}
Y.J. Sun {\it et al.},
\newblock ``New prototype multi-gap resistive plate chambers with long strips.''
\newblock {\em Nucl. Instr. Meth. A 593, 307 (2008)}.

\bibitem{MTDmrpc1}
Y. Wang {\it et al.},
\newblock ``Performance of a new LMRPC prototype for the STAR MTD system.''
\newblock {\em Nucl. Instr. Meth. A 640, 85 (2011)}.

\bibitem{TOFelectronics}
J.J. Schambach {\it et al.},
\newblock `Star Time of Flight Readout Electronics, Daq, and Cosmic Ray Test Stand.''
\newblock {\em Int. J. Mod. Phys. E 16, 2496 (2007)}.

\bibitem{HPTDC}
M. Mota {\it et al.},
\newblock ``A High-Resolution Time Interpolator Based on a Delay Locked Loop and an RC Delay Line.''
\newblock {\em IEEE J. Solid-State Circuits, Vol. 34, 10 (1999)}.

\bibitem{MTDcalib}
C. Yang {\it et al.},
\newblock ``Calibration and performance of the STAR Muon Telescope Detector using cosmic rays.''
\newblock {\em Nucl. Instr. Meth. A 762, 1 (2014)}.

\bibitem{MTDResultpp500}
R.R. Ma (for the STAR Collaboration),
\newblock ``Measurement of J/$\psi$ production in p + p collisions at $\sqrt{s_{NN}}$ = 500 GeV at STAR experiment.''
\newblock {\em Hard Probe 2015 proceedings}.

\bibitem{MTDResultAuAu200}
R.R. Ma (for the STAR Collaboration),
\newblock ``J/$\psi$ and $\varUpsilon$ measurements via the di-muon channel in Au + Au collisions at $\sqrt{s_{NN}}$ = 200 GeV with the STAR experiment.''
\newblock {\em Quark Matter 2015 proceedings}.

\bibitem{JpsiViaee0}
 L. Adamczyk {\it et al.} (STAR Collaboration),
\newblock ``J/$\psi$ production at low $p_{T}$ in Au + Au and Cu + Cu collisions at $\sqrt{s_{NN}}$ = 200 GeV with the STAR detector.''
\newblock {\em Phys. ReV. C 90, 024906 (2014)}.

\bibitem{JpsiViaee1}
 L. Adamczyk {\it et al.} (STAR Collaboration),
\newblock ``J/$\psi$ production at high transverse momenta in $p$ + $p$ and Au+Au collisions at $\sqrt{s_{NN}}$ = 200 GeV.''
\newblock {\em Phys. Lett. B 722, 55 (2013)}.

\bibitem{UpsilonWorldwide}
 W.M Zha {\it et al.},
\newblock ``Systematic study of the experimental measurements on ratios of different $\varUpsilon$ states.''
\newblock {\em Phys. ReV. C 88, 067901 (2013)}.

\bibitem{UpsilonSTAR}
 L. Adamczyk {\it et al.} (STAR Collaboration),
\newblock ``Suppression of $\varUpsilon$ production in $d$ + Au and Au + Au collisions at $\sqrt{s_{NN}}$ = 200 GeV.''
\newblock {\em  Phys. Lett. B 735, 127 (2014)}.

\bibitem{UpsilonCMS}
 S. Chatrchyan {\it et al.} (CMS Collaboration),
\newblock ``Observation of Sequential  $\varUpsilon$ Suppression in PbPb Collisions.''
\newblock {\em  Phys. Rev. Lett. 109, 222301 (2012)}.

%Chapter 4 (Analysis Details)
\bibitem{MCGlauber}
M.L. Miller {\it et al.},
\newblock ``Glauber Modeling in High-Energy Nuclear Collisions.''
\newblock {\em Annu. Rev. Nucl. Part. Sci. 57, 205 (2007)}.

\bibitem{dielectronJie}
J. Zhao,
\newblock ``Dielectron production at RHIC.”
\newblock {\em Ph. D. Thesis, Shanghai Institute of Applied Physics, CAS, (2013)}.

\bibitem{EventPlane0}
A. M. Poskanzer and S. A. Voloshin,
\newblock ``Methods for analyzing anisotropic flow in relativistic nuclear collisions.''
\newblock {\em Phys. Rev. C 58, 1671 (1998)}.

\bibitem{EventPlane1}
J. Adams {\it et al.} (STAR Collaboration),
\newblock ``Azimuthal anisotropy in Au + Au collisions at $\sqrt{s_{NN}}$ = 200 GeV.''
\newblock {\em Phys. Rev. C 72, 014904 (2005)}.

\bibitem{GEANT}
CERN Program Library Long Write-up W5013,
\newblock ``GEANT - Detector Simulation and Simulation Tool''
\newblock {\em http://wwwasdoc.web.cern.ch/wwwasdoc/geant\_html3/geantall.html}.

\bibitem{Pythia}
Torb\"orn Sj\"ostrand {\it et al.},
\newblock ``High-energy-physics event generation with Pythia 6.1.''
\newblock {\em  Comput. Phys. Commun. 135, 238 (2001)}.

\bibitem{UUEnergyDensity}
D. Kikola {\it et al.},
\newblock ``Prospects for quarkonia production studies in U + U collisions.''
\newblock {\em Phys. Rev. C 84, 054907 (2011)}.

\bibitem{TBW0}
Z. B. Tang {\it et al.},
\newblock ``Spectra and radial flow in relativistic heavy ion collisions with Tsallis statistics in a blast-wave description.''
\newblock {\em Phys. Rev. C 79, 051901 (2009)}.

\bibitem{TBW1}
Z. B. Tang {\it et al.},
\newblock ``The Statistical Origin of Constituent-Quark Scaling in QGP Hadronization.''
\newblock {\em Chin. Phys. Lett. 30, 031201 (2013)}.

\bibitem{IdentPartYieldsPRCLong}
B. I. Abelev {\it et al.} (STAR Collaboration),
\newblock ``Systematic measurements of identified particle spectra in $pp$, $d$ + Au , and
Au + Au collisions at the STAR detector.''
\newblock {\em Phys. Rev. C 79, 034909 (2009)}.

\bibitem{PDG}
K. A. Olive {\it et al.} (Particle Data Group),
\newblock ``REVIEW OF PARTICLE PHYSICS.''
\newblock {\em Chin. Phys. C 38, 090001 (2014)}.

\bibitem{KrollWada}
N. M. Kroll, W. Wada,
\newblock ``Internal Pair Production Associated with the Emission of High-Energy Gamma Rays.''
\newblock {\em Phys. Rev. 98, 1355 (1955)}.

\bibitem{pi0InvLamSqu}
K Nakamura {\it et al.},
\newblock ``Review of Particle Physics.''
\newblock {\em  J. Phys. G 37, 075021 (2010)}.

\bibitem{etaomegaInvLamSqu}
R. Arnaldi {\it et al.} (NA60 Collaboration),
\newblock ``Study of the electromagnetic transition form-factors in $\eta \rightarrow \mu^{+}\mu^{-}gamma$ and $\omega \rightarrow \mu^{+}\mu{-}\pi^{0}$ decays with NA60.''
\newblock {\em Phys. Lett. B 677, 260 (2009)}.

\bibitem{etaprimeInvLamSqu}
L.G. Landsberg,
\newblock ``Electromagnetic decays of light mesons.''
\newblock {\em  Phys. Rept. 128, 301 (1985)}.

\bibitem{phiInvLamSqu}
M. N. Achasov {\it et al.},
\newblock ``Study of conversion decays $\phi \rightarrow \eta e^{+}e^{-}$ and $\eta \rightarrow \gamma e^{+}e^{-}$ in the experiment with SND detector at VEPP-2M collider.''
\newblock {\em  Phys. Lett. B 504, 275 (2001)}.

\bibitem{charmedMesonpp}
L. Adamczyk {\it et al.} (STAR Collaboration),
\newblock ``Measurements of $D^{0}$ and $D^{*}$ production in $p$ + $p$ collisions at $\sqrt{s}$ = 200 GeV.''
\newblock {\em Phys. Rev. D 86, 072013 (2012)}.

\bibitem{charmedMesonAuAu}
L. Adamczyk {\it et al.} (STAR Collaboration),
\newblock ``Observation of $D^{0}$ Meson Nuclear Modifications in Au + Au Collisions at $\sqrt{s_{NN}}$ = 200 GeV.''
\newblock {\em Phys. Rev. Lett. 113, 142301 (2014)}.

%Chapter 5 (Results and discussion)
\bibitem{dielectoninUU193}
S. Yang (for the STAR Collaboration),
\newblock ``System-size and energy dependences of dielectron excess invariant mass spectra at STAR.''
\newblock {\em Quark Matter 2015 proceedings}.

\bibitem{STARUPCrho0}
C. Adler {\it et al.} (STAR Collaboration),
\newblock ``Coherent $\rho^{0}$ Production in Ultraperipheral Heavy-Ion Collisions.''
\newblock {\em 	Phys. Rev. Lett. 89, 272302 (2002)}.

\bibitem{STARUPCrho1}
B. I. Abelev {\it et al.} (STAR Collaboration),
\newblock ``$\rho^{0}$ photoproduction in ultraperipheral relativistic heavy ion collisions at $\sqrt{s_{NN}}$ = 200 GeV.''
\newblock {\em 	Phys. Rev. C 77, 034910 (2008)}.

\bibitem{PHENIXUPCjpsi}
S. Afanasiev {\it et al.} (PHENIX Collaboration),
\newblock ``Photoproduction of $J/\psi$ and of high mass $e^{+}e^{-}$ in ultra-peripheral Au + Au collisions at $\sqrt{s_{NN}}$ = 200 GeV.''
\newblock {\em 	Phys. Lett. B 679, 321 (2009)}.

\bibitem{ALICEUPCjpsi}
B. Abelev {\it et al.} (ALICE Collaboration),
\newblock ``Coherent $J/\psi$ photoproduction in ultra-peripheral Pb–Pb collisions
at $\sqrt{s_{NN}}$ = 2.76 TeV.''
\newblock {\em 	Phys. Lett. B 718, 1273 (2013)}.

\bibitem{ALICEUPCpsi2s}
J. Adam {\it et al.} (ALICE Collaboration),
\newblock ``Coherent  $\psi$(2S) photo-production in ultra-peripheral Pb–Pb collisions 
at $\sqrt{s_{NN}}$ = 2.76 TeV.''
\newblock {\em 	Phys. Lett. B 751, 358 (2015)}.

\bibitem{ALICEPCjpsi}
J. Adam {\it et al.} (ALICE Collaboration),
\newblock ``Measurement of an excess in the yield of $J/\psi$ at very low $p_{T}$ in Pb–Pb collisions at $\sqrt{s_{NN}}$ = 2.76 TeV.''
\newblock {\em arXiv:1509.08802 (2015)}.

%Chapter 6 (Gaseous detectors)
\bibitem{eic}
 A. Accardi {\it et al.},
\newblock ``Electron Ion Collider: The Next QCD Frontier - Understanding the glue that binds us all.''
\newblock {\em arXiv:1212.1701 (2012)}.

\bibitem{erhic}
 A. Accardi {\it et al.},
\newblock ``eRHIC Design Study: An Electron-Ion Collider at BNL.''
\newblock {\em arXiv:1409.1633 (2014)}.

\bibitem{estarloi}
The STAR Collaboration,
\newblock ``eSTAR: A Letter of Intent.''
\newblock {\em STAR Internal Note: SN0592 (2013)}.

\bibitem{startrdproposal}
The STAR Collaboration,
\newblock ``STAR Transition Radiation Detector Proposal.''
\newblock {\em https://wiki.bnl.gov/conferences/images/3/3d/TRD$\_$EIC$\_$RDproposal$\_$FY2012$\_$v3.pdf}.

\bibitem{thgem}
R. Chechik {\it et al.},
\newblock ``Thick GEM-like hole multipliers: properties and possible applications.''
\newblock {\em Nucl. Instr. Meth. A 535, 303 (2004)}.

\bibitem{thgem1}
A. Breskin {\it et al.},
\newblock ``A concise review on THGEM detectors.''
\newblock {\em Nucl. Instr. Meth. A 598, 107 (2009)}.

\bibitem{apv}
 M.J. French {\it et al.},
\newblock ``Design and results from the APV25, a deep sub-micron CMOS front-end chip for the CMS tracker.''
\newblock {\em Nucl. Instr. Meth. A 466, 359 (2001)}.
 
\bibitem{fgtreadout}
G.J. Visser {\it et al.},
\newblock ``A Readout System Utilizing the APV25 ASIC for the Forward GEM Tracker in STAR.'' 
\newblock {\em Real Time Conference (RT), 18th IEEE-NPSS, (2012) p1-6}.

\bibitem{driftv_data}
T. Zhao {\it et al.},
\newblock ``A Study of electron drift velocity in Ar-CO$_{2}$ gas mixtures.''
\newblock {\em Nucl. Instr. Meth. A 340, 485 (1994)}.

\bibitem{spatialResvsAngle}
F. Simon {\it et al.},
\newblock ``Beam Performance of Tracking Detectors with Industrially Produced GEM Foils.''
\newblock {\em Nucl. Instr. Meth. A 598, 432 (2009)}.

\bibitem{beijingSpe}
M. Ablikim{\it et al.},
\newblock ``Design and Construction of the BES\uppercase\expandafter{\romannumeral3} Detector.''
\newblock {\em Nucl. Instr. Meth. A 614, 345 (2010)}.

\bibitem{oldETOF}
S.H. An {\it et al.},
\newblock ``Testing the time resolution of the BES\uppercase\expandafter{\romannumeral3} end-cap TOF detectors.''
\newblock {\em Meas. Sci. Technol. 17 2650 (2006)}.

\bibitem{pikIdentification}
C. Zhao {\it et al.},
\newblock ``Time calibration for the end cap TOF system of BES\uppercase\expandafter{\romannumeral3}.''
\newblock {\em Chin. Phys. C 35, 72 (2011)}.

\bibitem{eTOFSimulation}
H. Zhang {\it et al.},
\newblock ``A GEANT4 simulation study of BES\uppercase\expandafter{\romannumeral3} endcap TOF upgrade.''
\newblock {\em Chin. Phys. C 37, 096002 (2013)}.

\bibitem{mrpc0}
E.C. Zeballos {\it et al.},
\newblock ``A very large multigap resistive plate chamber.''
\newblock {\em Nucl. Instr. Meth. A 434, 362 (1999)}.

\bibitem{mrpc1}
P. Fonte {\it et al.},
\newblock ``High-resolution RPCs for large TOF systems.''
\newblock {\em Nucl. Instr. Meth. A 449, 295 (2000)}.

\bibitem{mrpc2}
A. Akindinov {\it et al.},
\newblock ``Final test of the MRPC production for the ALICE TOF detector.''
\newblock {\em Nucl. Instr. Meth. A 602, 709 (2009)}.

\bibitem{positionDep}
N. Tomida {\it et al.},
\newblock ``High time resolution RPCs with different readout geometries.''
\newblock {\em  JINST 7, P12005 (2012)}.

%Chapter 7 (Summary and outlook)
\bibitem{ecooling}
A. V. Fedotov {\it et al.},
\newblock ``DESIGN ASPECTS OF AN ELECTROSTATIC ELECTRON COOLER FOR
LOW-ENERGY RHIC OPERATION.''
\newblock {\em Proceedings of 2011 Particle Accelerator Conference, New York, NY, USA}.

\bibitem{FixedTarget}
L. Adamczyk {\it et al.} (STAR Collaboration),
\newblock ``A fixed target program for STAR.''
\newblock {\em In preparation}.

\bibitem{iTPC}
L. Adamczyk {\it et al.} (STAR Collaboration),
\newblock ``Proposal for STAR Inner TPC Sector Upgrade (iTPC).''
\newblock {\em STAR Internal Note: SN0619 (2015)}.

\bibitem{eTOFLoI}
STAR and CBM Collaboration,
\newblock ``Letter of Interest: CBM TOF as STAR Endcap TOF for BES-II at RHIC.''
\newblock {\em STAR Internal Note: SN0639 (2015)}.

\bibitem{eTOFPhysics}
STAR and CBM Collaboration,
\newblock ``Physics Program for the STAR/CBM eTOF upgrade.''
\newblock {\em In preparation}.

\bibitem{CBMTof}
N. Herrmann,
\newblock ``Technical Design Report for the CBM Time-of-Flight System (TOF).''
\newblock {\em GSI Report GSI-2015-01999 (2014)}.

\bibitem{NA49proton}
C. Alt {\it et al.} (NA49 Collaboration),
\newblock ``Energy and centrality dependence of $\bar{p}$ and p production and the $\bar{\Lambda}/\bar{p}$ ratio in Pb + Pb collisions between 20A GeV and 158A GeV.''
\newblock {\em Phys. Rev. C 73, 044910 (2006)}.

\bibitem{NA49pion}
O. Chvala {\it et al.} (NA49 Collaboration),
\newblock ``Pion production in Pb + Pb collisions at the SPS.''
\newblock {\em Nucl. Phys. A 749, 304 (2005)}.

\end{thebibliography}
