
\chapter{Presentations and Publication List}

\noindent\textbf{Presentations：}

\begin{enumerate}

\item System-size and energy dependences of dielectron excess invariant mass spectra at STAR

XXV International Conference on Ultrarelativistic Nucleus-Nucleus Collisions (Quark Matter 2015), Sep.27 - Oct.3 2015, Kobe, Japan.

\end{enumerate}


\noindent\textbf{Publication List：}

\begin{enumerate}

\item {\it System-size and energy dependences of dielectron excess invariant mass spectra at STAR}

S. Yang (for the STAR Collaboration),  Nuclear Physics A (accepted)
 
\item {\it Cosmic ray test of mini-drift thick gas electron multiplier chamber for transition radiation detector}

S. Yang, S. Das, B. Buck, C. Li, T. Ljubicic, R. Majka, M. Shao, N. Smirnov, G. Visser, Z. Xu, Y. Zhou, Nucl. Instr. Meth. A 785, 33 (2015)

\item {\it Test of high time resolution MRPC with different readout modes for the BES\uppercase\expandafter{\romannumeral3} upgrade}

S. Yang, Y.J. Sun, C. Li, Y.K. Heng, S. Qian, H.F. Chen, T.X. Chen, H.L. Dai, H.H. Fan, S.B. Liu, S.D. Liu, X.S. Jiang, M. Shao, Z.B. Tang, H. Zhang, Z.G. Zhao, Nucl. Instr. Meth. A 763, 190 (2014)

\item {\it A prototype MRPC beam test for the BES\uppercase\expandafter{\romannumeral3} ETOF upgrade}

Yongjie Sun, Shuai Yang, Cheng Li, Sen Qian, Lailin Xu, Zaiwei Fu, Yuekun Heng, Hongfang Chen, Zebo Tang, Ming Shao, Huanhuan Liu, CPC (HEP \& NP) 36(5), 429 (2012)

\item {\it Systematic study of the experimental measurements on J/$\psi$ cross sections and kinematic distributions in p + p collisions at different energies}

Wangmei Zha, Bingchu Huang, Rongrong Ma, Lijuan Ruan, Zebo Tang, Zhangbu Xu, Chi Yang, Qian Yang, and Shuai Yang, Phys. Rev. C 93, 024919 (2016)

\item {\it MRPC detector for the BES\uppercase\expandafter{\romannumeral3} E-TOF upgrade}

R.X. Yang, C. Li, Y.J. Sun, H.F. Chen, H.L. Dai, Y.K. Heng, S.B. Liu, M. Shao, Z.B. Tang, Z. Wu, S. Yang, H. Zhang, JINST 9, C09032 (2014)

\item {\it Calibration and performance of the STAR Muon Telescope Detector using cosmic rays}

C. Yang, X.J. Huang, C.M. Du, B.C. Huang, Z. Ahammed, A. Banerjee, P. Bhattarari, S. Biswas, B. Bowen, J. Butterworth, M. Calderón de la Barca Sánchez, H. Carson, S. Chattopadhyay, D. Cebra, H.F. Chen, J.P. Cheng, M. Codrington, G. Eppley, C. Flores, F. Geurts, G.W. Hoffmann, A. Jentsch, A. Kesich, C. Li, Y.J. Li, W.J. Llope, S. Mioduszewski, Y. Mohamed, T. Nussbaum, A. Roy, L. Ruan, J.J. Schambach, Y.J. Sun, Y. Wang, K. Xin, Z. Xu, S. Yang, X.L. Zhu, Nucl. Instr. Meth. A 762, 1 (2014)

\item {\it Systematic study of the experimental measurements on ratios of different $\varUpsilon$ states}

Wangmei Zha, Chi Yang, Bingchu Huang, Lijuan Ruan, Shuai Yang, Zebo Tang, Zhangbu Xu, Phys. Rev. C 88, 067901 (2013)

\item {\it A GEANT4 simulation study of BES\uppercase\expandafter{\romannumeral3} endcap TOF upgrade}

Hui Zhang, Ming Shao, Cheng Li, Hongfang Chen, Yuekun Heng, Yongjie Sun, Zebo Tang, Changsheng Ji, Tianxiang Chen, Shuai Yang, CPC (HEP \& NP) 37(9), 096002 (2013)

\item {\it The high timing resolution $T_{0}$ system in IHEP E3 beam line}

S. Qian, Y. Wang, Z. Ning, X. Wang, Z. Fu, S. Liu, Z. Wang, X. Chen, S. Yang, Y. Heng, Y. Zhen, M. Qi, T. Zhao, C. Li, JINST 7, P02013 (2012)

\item {\it Cosmic ray test for a $T_{0}$ detector}

Zaiwei Fu, Sen Qian, Zhe Ning, Shudong Liu, Xiaohui Chen, Yuekun Heng, Yifang Wang, Ming Qi, Shuai Yang, Yongjie Sun, Ming Shao, Cheng Li, Yangheng Zheng, CPC (HEP \& NP) 35(10), 946 (2011)

\end{enumerate}

\noindent\textbf{STAR Publications as active Author (Dilepton relevant)：}

\begin{enumerate}

\item Measurements of Dielectron Production in Au+Au Collisions at $\sqrt{s_{NN}} =$ 200 GeV from the STAR Experiment.

L. Adamczyk {\it et al.} (STAR Collaboration), Phys. Rev. C 92, 24912 (2015)

\item Energy dependence of acceptance-corrected dielectron excess mass spectrum at mid-rapidity in Au+Au collisions at $\sqrt{s_{NN}}$ = 19.6 and 200 GeV.

 L. Adamczyk {\it et al.} (STAR Collaboration), Phys. Lett. B 750, 64 (2015)

\end{enumerate}